Utilizing Convolution for Obstacle Avoidance during Robotic Manipulator Movement

### 2023-07-18 Articles/ERK/erk.tex
article structure

\begin{document}
%make title
\title{Navodila in osnutek prispevka za konferenco ERK 2014}

\author{Prvi Avtor$^{1}$, Drugi Avtor$^{2}$} % use ^1, ^2 for author(s) from different institutions

\affiliation{$^{1}$Ime in naslov organizacije prvega avtorja\\ 
$^{2}$Ime in naslov organizacije drugega avtorja, če je drugačna od prvega }

\email{E-pošta: avtor@naslov.com}

@@

\begin{abstract}{Instructions and Template for ERK 2014 Conference}
For the papers written in Slovene language an English title and abstract is required. The abstract should be no more than 200 words.

@@

\section{Uvod}

@@

>>>>

\begin{document}
%make title
\title{Utilizing Convolution for Obstacle Avoidance during Robotic Manipulator Movement}

\author{Jakob Baumgartner$^{1}$, Gregor Klančar$^{2}$} % use ^1, ^2 for author(s) from different institutions

\affiliation{$^{1}$Fakulteta za Elektrotehniko, Tržaška cesta 25, 1000 Ljubljana\\}

\email{E-pošta: jakob.baumgartner@fe.uni-lj.si}

@@

\begin{abstract}{Abstract}
For the papers written in Slovene language an English title and abstract is required. The abstract should be no more than 200 words.

@@

\section{Introduction }

@@

\section{Background and Related Work}

\section{Methodology }

\subsection{Obstacle Grid}

\subsection{Convolution Techniques}

\subsection{Robot Segments Control}

\section{Experiment and Results}
